---
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    theme: flatly
    number_sections: false
    self_contained: false
    lib_dir: ../../docs/countries/libs
    includes:
      in_header: ../../docs/resources/header.html
      after_body: ../../docs/resources/footer.html
params:
  country: Afghanistan
title: "National Perspective Daily Update"
subtitle: "`r params$country`"
---

```{r setup, include=F}
# Set R Markdown Options
knitr::opts_chunk$set(echo = F, 
                      message = F, 
                      warning = F,
                      echo = FALSE,
                      fig.align = "center",
                      out.width = "100%")

# Avoid numbers being rounded
options(scipen = 999)

# Laod packages
library(here)
library(readr)
library(tidyverse)
library(sf)
library(maps)
library(gganimate)
library(patchwork)
library(ggthemr)
library(grid)
library(magick)
library(plotly)
library(emojifont)

library(shiny)
library(shinydashboard)

# Load functions stored in functions file
files.sources = list.files(here::here("functions"))
invisible(sapply(files.sources, function(x) source(here::here("functions", x))))

# Setup captions
caption <- glue::glue("Data Source: John Jopkins University
                         Data updated on {date}
                         CC BY 4.0 Michael Harper 2020 www.coviz.info", date = format(Sys.time(), '%d %B %Y'))

current_date <- glue::glue("Data updated on {date}", date = format(Sys.time(), '%d %B %Y'))

# Setup Text
df <- readr::read_csv(here::here("data/global/covid_data_global.csv"),
                      col_types = readr::cols()) %>%
  mutate(continent = factor(continent, levels = rev(c("Asia", "Europe", "North America", "South America", "Africa", "Oceania"))))

df_all <- loadData(spatial = T)
world_map <- loadWorldMap()
```

```{r}
df_country <- df_all %>%
  filter(region == params$country)

# Calculate metrics
deaths <-
  df_country %>%
  filter(date == max(date)) %>%
  filter(type == "deaths") %>%
  pull(value)

deaths_7_days_ago <- 
  df_country %>%
  filter(date == max(df$date) - lubridate::ddays(7)) %>%
  filter(type == "deaths") %>%
  pull(value)

# Calculate metrics
recovered <-
  df_country %>%
  filter(date == max(date)) %>%
  filter(type == "recovered") %>%
  pull(value)

cases <- 
  df_country %>%
  filter(date == max(date)) %>%
  filter(type == "cases") %>%
  pull(value)

cases_7_days_ago <-
  df_country %>%
  filter(date == max(df$date) - lubridate::ddays(7)) %>%
  filter(type == "cases") %>%
  pull(value)


increasePercentageCases <- scales::percent(cases/cases_7_days_ago)
increasePercentageDeaths <- scales::percent(deaths/deaths_7_days_ago)
```

```{block2, type = "rmdimportant", echo = T}
Note, the country statistics are in beta development. More features will be added over the coming week. Make sure to check back for more details and statistics
```

There are **`r cases`** recorded cases and **`r deaths`** recorded deaths. In the past 7 days, this has increase by **`r increasePercentageCases`** and **`r increasePercentageDeaths`** respectively. 

```{r}
fluidRow(
    infoBox(
      "Confirmed Cases", cases, icon = icon("users"), color = "blue", fill = TRUE
    ),
    infoBox(
      "Deaths", deaths, icon = icon("users"), color = "red",
      fill = TRUE
    ),
    infoBox(
      "Recovered", recovered, icon = icon("hospital"), color = "green",
      fill = TRUE
    )
)
```

##  {.tabset}

### Logarithmic

```{r plotCumulativeCasesandDeaths, fig.cap = "Cumulative number of cases"}
p1 <- 
    df_country %>%
  filter(type != "recovered") %>%
  ggplot(aes(x = date, y = value, colour = type)) +
  geom_line() +
  geom_point(aes(text = paste0(stringr::str_to_title(type), ": ", value))) +
  labs(title = glue::glue("Cumulative Cases and Deaths in {country}", country = params$country),
       subtitle = glue::glue("Logarithmic scale enables us to understand the exponential growth better
                             Data accurate as of {date}", date = max(df_country$date)),
       colour = "Type",
       y = "Count",
       x = "Date",
       caption = caption) +
  theme(legend.position = "right",
        panel.grid.minor.y = element_line(linetype = "solid", colour = "grey90", size = 0.1),
        plot.caption = element_text(size = rel(0.7))) +
  scale_y_log10(minor_breaks = c(c(1:9) *10, c(1:9) *100, c(1:9) *1000, c(1:10) *10000, c(1:10) *100000),
                breaks = c(100, 1000, 10000, 100000, 1000000))
p1
```

### Linear

```{r plotCumulativeLinear, fig.cap = "Cumulative number of cases"}
p2 <- ggplot(df_country, aes(x = date, y = value, colour = type)) +
  geom_line() +
  labs(title = glue::glue("Cumulative Cases and Deaths in {country}", country = params$country),
       subtitle = glue::glue("Linear plots make it hard to visualise whether the exponential growth is being controlled
                             Data accurate as of {date}", date = max(df_country$date)),
       colour = "Type",
       y = "Count",
       x = "Date",
       caption = caption) +
  theme(legend.position = "right",
        plot.caption = element_text(size = rel(0.7)))
p2
```


```{r}
p2 <- 
  df_country %>%
  filter(type != "recovered") %>%
  ggplot(aes(x = date, y = value, colour = type)) +
  geom_line() +
  labs(title = glue::glue("Cumulative Cases and Deaths for {country}", country = params$country),
       subtitle = glue::glue("Total number of confirmed cases: {cases}
       Total number of deaths: {deaths}", deaths = deaths, cases = cases)) +
  theme(legend.position = "right",
        panel.grid.minor = element_line(linetype = "dashed", colour = "grey90", size = 0.4),
        panel.grid.major = element_line(linetype = "solid", colour = "grey90")) +
  scale_y_log10(minor_breaks = c(c(1:9), c(1:9) *10, c(1:9) *100, c(1:9) *1000, c(1:9) *10000))
p2
```

```{r fig.height=4, fig.width=6}

# Only show since 200th outbreak
df_country_bar <- df_country %>%
  filter(daysSince200Outbreak > 0)

if(nrow(df_country_bar) > 0){
  
  p2 <- ggplot(df_country_bar) + 
  geom_col(aes(x = date, y = changeDaily, fill = type), colour = "grey90") +
  labs(title = "Daily number of recorded cases and deaths",
       y = "Number",
       x = "Date",
       subtitle = glue::glue("Total number of confirmed cases: {cases}
       Total number of deaths: {deaths}", deaths = deaths, cases = cases)) +
  facet_grid(type~., scales = "free_y", labeller = labeller(type = function(x) tools::toTitleCase(x))) +
  scale_y_continuous(expand = c(0.1,0.1)) + 
  theme(panel.grid.major.x = element_blank(),
        legend.background = element_blank(),
        legend.position = "none")

p2
  
}


```


```{r results="asis"}
# Make metadata

library(metathis)
meta() %>%
  meta_description(
    "Daily Updating Summary of the COVID-19 Outbreak"
  ) %>% 
  meta_name() %>% 
  meta_viewport() %>% 
  meta_social(
    title = glue::glue("COVID-19 Data Visualisations for {country}", country = params$country),
    url = "www.coviz.info",
    image = "https://github.com/dr-harper/Covid19/blob/master/docs/summary_files/figure-html/plotLogarithmic-1.png?raw=true",
    image_alt = "Growth Rates of COVID-19",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@DrMichaelHarper", 
    og_type = "website", 
    og_locale = "en_UK", 
    og_site_name = "COVID-19 Visualisation", 
    og_author = "Michael Harper")

# Add additional opengraph specs
openGraph <- list(
  htmltools::tags$meta(property = "og:site_name", content = "COVID-19 Visualisation"),
  htmltools::tags$meta(property = "og:title", content = glue::glue("COVID-19 Data Visualisations for {country}", country = params$country)),
  htmltools::tags$meta(property = "og:type", content = "website"),
  htmltools::tags$meta(property = "article:modified_time", content = Sys.Date()),
  htmltools::tags$meta(property = "og:description", content = "Up to date data visualisations of the COVID-19 pandemic"),
  htmltools::tags$meta(property = "og:url", content = "www.coviz.info"),
  htmltools::tags$meta(property = "og:image", content = "https://github.com/dr-harper/Covid19/blob/master/docs/summary_files/figure-html/plotLogarithmic-1.png?raw=true")
)
as_meta(openGraph)
```

# Feedback and Support

Have any graphs you would like to see made in this website? [Reach out to me](about) with suggestions and I would love to add them! This analysis is all done as voluntary work around my job, and I am competing to get time to support this work. If you would like to show your gratitude, it would be great if you could [donate](https://www.paypal.me/mikeyharper) to support this effort.

<style>.bmc-button img{height: 34px !important;width: 35px !important;margin-bottom: 1px !important;box-shadow: none !important;border: none !important;vertical-align: middle !important;}.bmc-button{padding: 7px 10px 7px 10px !important;line-height: 35px !important;height:51px !important;min-width:217px !important;text-decoration: none !important;display:inline-flex !important;color:#ffffff !important;background-color:#79D6B5 !important;border-radius: 5px !important;border: 1px solid transparent !important;padding: 7px 10px 7px 10px !important;font-size: 22px !important;letter-spacing: 0.6px !important;box-shadow: 0px 1px 2px rgba(190, 190, 190, 0.5) !important;-webkit-box-shadow: 0px 1px 2px 2px rgba(190, 190, 190, 0.5) !important;margin: 0 auto !important;font-family:'Cookie', cursive !important;-webkit-box-sizing: border-box !important;box-sizing: border-box !important;-o-transition: 0.3s all linear !important;-webkit-transition: 0.3s all linear !important;-moz-transition: 0.3s all linear !important;-ms-transition: 0.3s all linear !important;transition: 0.3s all linear !important;}.bmc-button:hover, .bmc-button:active, .bmc-button:focus {-webkit-box-shadow: 0px 1px 2px 2px rgba(190, 190, 190, 0.5) !important;text-decoration: none !important;box-shadow: 0px 1px 2px 2px rgba(190, 190, 190, 0.5) !important;opacity: 0.85 !important;color:#ffffff !important;}</style><link href="https://fonts.googleapis.com/css?family=Cookie" rel="stylesheet"><a class="bmc-button" target="_blank" href="https://www.buymeacoffee.com/BXFAIV5"><img src="https://cdn.buymeacoffee.com/buttons/bmc-new-btn-logo.svg" alt="Buy me a coffee"><span style="margin-left:15px;font-size:28px !important;">Buy me a coffee</span></a>


# Comments

<script id="dsq-count-scr" src="//coviz-info.disqus.com/count.js" async></script>

<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://coviz-info.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
                            


