---
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
params:
  country: Nigeria
title: "`r glue::glue('{country} COVID-19 Statistics', country = params$country)`"
---

```{r setup, include=F}
# Set R Markdown Options
knitr::opts_chunk$set(echo = F, 
                      message = F, 
                      warning = F,
                      echo = FALSE,
                      fig.align = "center",
                      out.width = "100%",
                      dev = "svg")

# Avoid numbers being rounded
options(scipen = 999)

# Laod packages
library(here)
library(readr)
library(tidyverse)
library(sf)
library(maps)
library(gganimate)
library(patchwork)
library(ggthemr)
library(grid)
library(magick)
library(plotly)
library(emojifont)

library(shiny)
library(shinydashboard)

# devtools::install_github('cttobin/ggthemr')
ggthemr("light", type = 'inner')

# Load functions stored in functions file
files.sources = list.files(here::here("functions"))
invisible(sapply(files.sources, function(x) source(here::here("functions", x))))

# Setup captions
caption <- glue::glue("Data Source: Johns Hopkins University
                        Michael Harper 2020 www.coviz.info", date = format(Sys.time(), '%d %B %Y'))

current_date <- glue::glue("Data updated on {date}", date = format(Sys.time(), '%d %B %Y'))

# Setup Text
df <- readr::read_csv(here::here("data/global/covid_data_global.csv"),
                      col_types = readr::cols()) %>%
  mutate(continent = factor(continent, levels = rev(c("Asia", "Europe", "North America", "South America", "Africa", "Oceania"))))

df_all <- loadData(spatial = T)
world_map <- loadWorldMap()


# Define the colour palette for the plot
set_swatch(c(
  "#785d37",
  "#62bba5", "#ffb84d",
  "#aaa488", "#b2432f",
  "#3a6589", "#9b5672",
  "#908150", "#373634", 
  "#569b7f", "#292217"
))

```


```{r fig.height=2.5, fig.width=6, paged.print=FALSE}
mapCountry <- world_map %>%
  filter(region == params$country)

if(nrow(mapCountry) > 0){
  
  mapContinent <- world_map %>%
    filter(continent == mapCountry$continent)
  
  bbox <- sf::st_bbox(mapCountry) %>% as.numeric()
  
  ggplot() +
    geom_sf(data = world_map, fill = "grey95", colour = "grey95") +
    geom_sf(data = mapContinent, fill = "grey90", colour = "grey90")  +
    geom_sf(data = mapCountry, fill = "#3a6589", colour = NA) +
    theme(plot.caption = element_text(size = rel(0.5)),
          plot.background = element_rect(fill = NA, colour = NA),
          panel.background = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.line = element_blank(),
          axis.title = element_blank(),
          panel.grid = element_blank(),
          legend.background = element_blank(),
          title = element_text(colour = '#706f6f', size = rel(2), hjust = 0.5),
          plot.title = element_text(colour = '#706f6f', size = rel(1.5), hjust = 0.5),
          legend.position = "none")
  
}

```



```{r}
# Select data for the reference country only
df_country <- df_all %>%
  filter(region == params$country)

# Custom function to calculate indicators
metrics <- summaryIndicators(df_country)

country_rank <- df_all %>%
  group_by(region) %>%
  filter(date == max(date)) %>%
  ungroup() %>%
  filter(type == "deaths") %>%
  mutate(rank = min_rank(-value))


globalRank <- country_rank %>%
  filter(region == params$country) %>%
  pull(rank)

```

This web page provides daily updating statistics for the COVID-19 pandemic. As of `r format(Sys.time(), '%d %B, %Y')`, the `r params$country` has **`r metrics$cases`** recorded cases and **`r metrics$deaths`** recorded deaths. In the past 7 days, this has increase by **`r metrics$increasePercentageCases`** and **`r metrics$increasePercentageDeaths`** respectively.

```{r}
fluidRow(
  infoBox(
    "Confirmed Cases", metrics$cases, icon = icon("users"), color = "blue", fill = TRUE
  ),
  infoBox(
    "Deaths", metrics$deaths, icon = icon("users"), color = "red",
    fill = TRUE
  ),
  infoBox(
    "Recovered", metrics$recovered, icon = icon("hospital"), color = "green",
    fill = TRUE
  ),
  infoBox(
    "Number of Deaths Rank Globally",  scales::ordinal(globalRank), icon = icon("hospital"), color = "purple",
    fill = TRUE
  )
)
```

Figure \@ref(fig:plotCumulativeCasesandDeaths) shows the global trend in Coronavirus cases. Note it is plotted on a **logarithmic scale**: this is much more useful than a linear plot and fortunately are being increasingly used to display the statistics of the outbreak.. In situations like this where we are dealing with a exponential growth, logarithmic plots enable us to easily visualise the rate of change much easier. Plotted on this, we transform the exponential curve into a straight line. If the line gets steeper, it means the virus is spreading quicker, while reducing the gradient shows that the virus is getting under control.

##  {.tabset}

### Logarithmic

```{r plotCumulativeCasesandDeaths, fig.cap = "Cumulative number of cases"}
p1 <- 
  df_country %>%
  filter(type != "recovered") %>%
  ggplot(aes(x = date, y = value, colour = type)) +
  geom_line(size = 1.4) +
  geom_point(aes(text = paste0(stringr::str_to_title(type), ": ", value))) +
  labs(title = glue::glue("Cumulative Cases and Deaths in {country}", country = params$country),
       subtitle = "Logarithmic scale enables us to understand the exponential growth better",
       colour = "Type",
       y = "Count",
       x = "Date",
       caption = caption) +
  theme(legend.position = "top",
        panel.grid.minor.y = element_line(linetype = "solid", colour = "grey90", size = 0.1),
        plot.caption = element_text(size = rel(0.7))) +
  scale_y_log10(minor_breaks = c(c(1:9) *10, c(1:9) *100, c(1:9) *1000, c(1:10) *10000, c(1:10) *100000),
                breaks = c(10, 100, 1000, 10000, 100000, 1000000),
                limits = (c(1, max(df_country$value))* 2),
                expand = c(0,0))
p1
```

### Linear

```{r plotCumulativeLinear, fig.cap = "Cumulative number of cases"}
p2 <- 
  df_country %>%
  filter(type != "recovered") %>%
  ggplot(aes(x = date, y = value, colour = type)) +
  geom_line(size = 1.4) +
  labs(title = glue::glue("Cumulative Cases and Deaths in {country}", country = params$country),
       subtitle = glue::glue("Linear plots make it hard to visualise whether the exponential growth is being controlled"),
       colour = "Type",
       y = "Count",
       x = "Date",
       caption = caption) +
  theme(legend.position = "top",
        plot.caption = element_text(size = rel(0.7)))
p2
```

# Comparison Against other countries

Although cases may be more useful to understand the scale of the outbreak, it can be difficult to compare countries as there are [very different testing schemes](https://ourworldindata.org/covid-testing). The numbers of deaths give a more consistent comparison of statistics if we are trying to understand differences internationally, which are more consistently recorded. Using the deaths, we can understand the rate of spread of the virus, although it should be aware that deaths will typically occur around two weeks after infection. It therefore mean deaths lag behind any changes in public policy, so when governments introduce any measures, there will be a delay in when they see the impact within the data.

```{r plotLogarithmic, fig.height=5, fig.width=8}

# Function to easily produce straight lines on logarithmic plot
growthRate <- function(doubleEvery, days, start = 10) {
  start * 2**((days) / doubleEvery)
}

# Calculate the lines
lines <- data.frame(x = 0:50) %>%
  mutate(
    y1 = growthRate(1, x),
    y2 = growthRate(2, x),
    y3 = growthRate(3, x),
    y7 = growthRate(7, x)
  ) %>%
  gather(key = y, value = "values", -x)

# Have to manually specify angle as this depends on the graph aspect ratio, so cannot easily be calculated
labels <- data.frame(
  x = c(10, 20, 32, 35),
  y = c(growthRate(1, 10), growthRate(2, 20), growthRate(3, 32), growthRate(7, 35)),
  label = c("Doubles Daily", "... every 2 Days", "... every 3 Days", ". every  Week"),
  angle = c(60, 45, 34, 16)
)

# Prepare the data
df_plot2 <-
  df_all %>%
  filter(type == "deaths") %>%
  filter(daysSince10Deaths >= 0) %>%
  filter(region != "Cruise Ship") %>%
  group_by(region) %>%
  mutate(numdaysMax = max(daysSince10Deaths)) %>%
  filter(daysSince10Deaths <= 50)

# List key countries
# Deselect if key country is also the country being displayed
keyCountries <- c("UK", "US", "Italy", "Spain", "France", "South Korea", "China", "Germany", "Japan", "Iran")
dropMatching <- keyCountries[!(keyCountries %in% params$country)]

df2_plot2 <- df_plot2 %>%
  rename("area" = "region") %>%
  filter(area %in% dropMatching)

df3_plot2 <- df2_plot2 %>%
  group_by(area) %>%
  filter(date == max(date))

df_selectedcountry_plot2 <- df_plot2 %>%
  rename("area" = "region") %>%
  filter(area == params$country)

df2_selectedcountry_plot2 <- df_selectedcountry_plot2 %>%
  group_by(area) %>%
  filter(date == max(date))

baseplot <- 
  ggplot(mapping = aes(x = daysSince10Deaths, y = value)) +
  # Show growth lines
  annotate(geom = "text", x = labels$x, y = labels$y, label = labels$label, angle = labels$angle, colour = "grey50", vjust = -1) +
  geom_line(data = lines, aes(x, values, group = y), linetype = "dashed", colour = "grey50") +
  # Show background data for other countries
  geom_point(data = df2_plot2, aes(group = area), colour = "grey70", size = 1.2) +
  geom_line(data = df2_plot2, aes(group = area), colour = "grey70", size = 1.2) +
  # Show label for other countries
  geom_point(data = df3_plot2, aes(colour = area)) +
  geom_text(data = df3_plot2, aes(label = area, colour = area), vjust = 2) +
  # Show data for selected country
  geom_point(data = df_selectedcountry_plot2, aes(group = area, colour = region), colour = "#3a6589", size = 1.4) +
  geom_line(data = df_selectedcountry_plot2, aes( group = area), colour = "#3a6589", size = 1.4) +
  # Show label for selected country
  geom_point(data = df2_selectedcountry_plot2, colour = "#3a6589", size = 2) +
  geom_label(data = df2_selectedcountry_plot2, aes(label = area), colour = "#3a6589", vjust = -1) +
  labs(x = "Days Since 10th Death",
       y = "Cumulative Number of Deaths",
       fill = "Country",
       title = glue::glue("COVID-19 related deaths: {country} vs. other countries", country = params$country),
       caption = paste0(caption, "\nDesign inspired by Financial Times")) +
  scale_y_log10(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0), breaks = c(0, 7, 14, 21, 28, 35, 42, 49)) +
  coord_cartesian(xlim = c(0, 50), ylim = c(10, 50000)) +
  theme(
    panel.grid.minor = element_line(linetype = "dashed", colour = "grey90"),
    legend.position = "none"
  )

if(nrow(df_selectedcountry_plot2) == 0) baseplot <- baseplot + labs(subtitle = glue::glue("{country} has yet to have 10 deaths and therefore is not displayed", country = params$country))


baseplot

```


# Daily Count


```{r fig.height=6, fig.width=8}

# Only show since 200th outbreak
df_country_bar <- df_country %>%
  filter(daysSinceOutbreak > 0)

# If more than 200 cases, it is better to skip these as there is noise
if(nrow(df_country_bar) < 45) df_country_bar <- df_country

df_country_bar <- 
  df_country_bar %>%
  mutate(type = tools::toTitleCase(type))

plot_labels <- df_country_bar %>%
  group_by(type) %>%
  summarise(maxValue = 0.9 * max(changeDaily, na.rm = T),
            minDate = min(date),
            total = max(value)) %>%
  mutate(minDate = min(minDate),
         maxAll = max(maxValue),
         label = glue::glue("{type}: {total}"))

int_breaks <- function(x, n = 5) pretty(x, n)[pretty(x, n) %% 1 == 0] 

p2 <- ggplot(df_country_bar) + 
  geom_col(aes(x = date, y = changeDaily, fill = type), colour = "grey90") +
  labs(title = glue::glue("{country} daily statistics for COVID-19", country = params$country),
       subtitle = glue::glue("Information as of {date}", date = format(Sys.time(), '%d %B %H:00')),
       y = "Number",
       x = "Date",
       caption = caption) +
  geom_label(data = plot_labels, aes(x = minDate, y = maxValue, label = label, fill = type), 
             hjust = 0, label.r = unit(0, "mm"), label.size = 0.2, alpha = 0.5) +
  facet_grid(type~., scales = "free_y") +
  scale_y_continuous(expand = c(0.1,0.1), breaks = int_breaks) + 
  scale_x_datetime(date_breaks = "1 week", date_labels = "%d %b") +
  theme(panel.grid.major.x = element_blank(),
        legend.background = element_blank(),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.y = element_blank())
p2

```


```{r plotPercent, fig.height=5, fig.width=8}

# Prepare the data
df_plot2 <-
  df_all %>%
  filter(type == "deaths") %>%
  filter(daysSince10Deaths >= 0) %>%
  filter(region != "Cruise Ship") %>%
  group_by(region) %>%
  mutate(numdaysMax = max(daysSince10Deaths)) %>%
  filter(daysSince10Deaths <= 60) %>%
  mutate(changeDailyPercSmooth  = (changeDailyPerc + lag(changeDailyPerc, 1) + lag(changeDailyPerc, 2))/3)

# List key countries
# Deselect if key country is also the country being displayed
keyCountries <- c("UK", "US", "Italy", "Spain", "France", "South Korea", "China", "Germany", "Japan", "Iran")
dropMatching <- keyCountries[!(keyCountries %in% params$country)]

df2_plot2 <- df_plot2 %>%
  rename("area" = "region") %>%
  filter(area %in% dropMatching)

df3_plot2 <- df2_plot2 %>%
  group_by(area) %>%
  filter(date == max(date))

df_selectedcountry_plot2 <- df_plot2 %>%
  rename("area" = "region") %>%
  filter(area == params$country)

df2_selectedcountry_plot2 <- df_selectedcountry_plot2 %>%
  group_by(area) %>%
  filter(date == max(date))

baseplot <- 
  ggplot(mapping = aes(x = daysSince10Deaths, y = changeDailyPercSmooth)) +
  # Show background data
  geom_point(data = df2_plot2, aes(group = area, colour = area), alpha = 0.4, size = 0.8) +
  geom_line(data = df2_plot2, aes(group = area, colour = area), alpha = 0.4, size = 0.8) +
  # Show label
  geom_point(data = df3_plot2, aes(colour = area)) +
  geom_label(data = df3_plot2, aes(x = ifelse(daysSince10Deaths > 50, 50, daysSince10Deaths),
                                   label = area, colour = area), hjust = -0.1, vjust = 0, alpha = 0.4) +
  # Show selected country
  geom_point(data = df_selectedcountry_plot2, aes(group = area), colour = "#3a6589", size = 1.4) +
  geom_line(data = df_selectedcountry_plot2, aes( group = area), colour = "#3a6589", size = 1.4) +
  # Show label selected countrys
  geom_point(data = df2_selectedcountry_plot2, colour = "#3a6589", size = 2) +
  geom_label(data = df2_selectedcountry_plot2, aes(label = area), colour = "#3a6589", hjust = -0) +
  labs(x = "Days since 10th Death",
       y = "% Change in deaths",
       fill = "Country",
       title = glue::glue("COVID-19 daily change in deaths: {country} vs. other countries", country = params$country),
       subtitle = "3 day moving average of the number of deaths",
       caption = caption) +
  scale_x_continuous(expand = c(0, 0), breaks = c(0, 7, 14, 21, 28, 35, 42, 49)) +
  coord_cartesian(xlim = c(0, 55)) +
  theme(
    panel.grid.minor = element_line(linetype = "dashed", colour = "grey90"),
    legend.position = "none"
  )

if(nrow(df_selectedcountry_plot2) == 0) baseplot <- baseplot + labs(subtitle = glue::glue("{country} has yet to have 10 deaths and therefore is not displayed", country = params$country))


baseplot

```


```{block2, type = "rmdinfo", echo = T}
More charts will be added in the next few days. Make sure to check back for updates.
```

# Data


This analysis is largely based on the Johns Hopkins Novel Coronavirus Dataset, which is [available here](https://github.com/CSSEGISandData/COVID-19/blob/master/README.md). It is an aggregation of a range of different Coronavirus datasets, and is seen as the best globally available. Countries may offer high resolution datasets, but these are not always made publicly available in an easy format, so may not make it into the dataset. It is possible that better data is available for your country of selection.

```{r results="asis"}
# Make metadata

library(metathis)
meta() %>%
  meta_description(
    "Daily Updating Summary of the COVID-19 Outbreak"
  ) %>% 
  meta_name() %>% 
  meta_viewport() %>% 
  meta_social(
    title = glue::glue("COVID-19 Data Visualisations for {country}", country = params$country),
    url = "www.coviz.info",
    image = "https://github.com/dr-harper/Covid19/blob/master/docs/summary_files/figure-html/plotLogarithmic-1.png?raw=true",
    image_alt = "Growth Rates of COVID-19",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@DrMichaelHarper", 
    og_type = "website", 
    og_locale = "en_UK", 
    og_site_name = "COVID-19 Visualisation", 
    og_author = "Michael Harper")

# Add additional opengraph specs
openGraph <- list(
  htmltools::tags$meta(property = "og:site_name", content = "COVID-19 Visualisation"),
  htmltools::tags$meta(property = "og:title", content = glue::glue("COVID-19 Data Visualisations for {country}", country = params$country)),
  htmltools::tags$meta(property = "og:type", content = "website"),
  htmltools::tags$meta(property = "article:modified_time", content = Sys.Date()),
  htmltools::tags$meta(property = "og:description", content = "Up to date data visualisations of the COVID-19 pandemic"),
  htmltools::tags$meta(property = "og:url", content = "www.coviz.info"),
  htmltools::tags$meta(property = "og:image", content = "https://github.com/dr-harper/Covid19/blob/master/docs/summary_files/figure-html/plotLogarithmic-1.png?raw=true")
)
as_meta(openGraph)
```

# Feedback and Support

Have any graphs you would like to see made in this website? [Reach out to me](about) with suggestions and I would love to add them! This analysis is all done as voluntary work around my job, and I am competing to get time to support this work. If you would like to show your gratitude, it would be great if you could [donate](https://www.paypal.me/mikeyharper) to support this effort.

<style>.bmc-button img{height: 34px !important;width: 35px !important;margin-bottom: 1px !important;box-shadow: none !important;border: none !important;vertical-align: middle !important;}.bmc-button{padding: 7px 10px 7px 10px !important;line-height: 35px !important;height:51px !important;min-width:217px !important;text-decoration: none !important;display:inline-flex !important;color:#ffffff !important;background-color:#79D6B5 !important;border-radius: 5px !important;border: 1px solid transparent !important;padding: 7px 10px 7px 10px !important;font-size: 22px !important;letter-spacing: 0.6px !important;box-shadow: 0px 1px 2px rgba(190, 190, 190, 0.5) !important;-webkit-box-shadow: 0px 1px 2px 2px rgba(190, 190, 190, 0.5) !important;margin: 0 auto !important;font-family:'Cookie', cursive !important;-webkit-box-sizing: border-box !important;box-sizing: border-box !important;-o-transition: 0.3s all linear !important;-webkit-transition: 0.3s all linear !important;-moz-transition: 0.3s all linear !important;-ms-transition: 0.3s all linear !important;transition: 0.3s all linear !important;}.bmc-button:hover, .bmc-button:active, .bmc-button:focus {-webkit-box-shadow: 0px 1px 2px 2px rgba(190, 190, 190, 0.5) !important;text-decoration: none !important;box-shadow: 0px 1px 2px 2px rgba(190, 190, 190, 0.5) !important;opacity: 0.85 !important;color:#ffffff !important;}</style><link href="https://fonts.googleapis.com/css?family=Cookie" rel="stylesheet"><a class="bmc-button" target="_blank" href="https://www.buymeacoffee.com/BXFAIV5"><img src="https://cdn.buymeacoffee.com/buttons/bmc-new-btn-logo.svg" alt="Buy me a coffee"><span style="margin-left:15px;font-size:28px !important;">Buy me a coffee</span></a>


# Comments

<script id="dsq-count-scr" src="//coviz-info.disqus.com/count.js" async></script>

<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://coviz-info.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>



